---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  cache = TRUE,
  collapse = TRUE,
  comment = "#>"
)
```

# sheffield_cycle_data

<!-- badges: start -->
<!-- badges: end -->

The goal of sheffield_cycle_data is to get started with key datasets on cycling, infrastructure, behaviour and maybe more.

## Set-up and packages

There are a number of packages that can help get transport (including cycling) data.
Install them as follows:

```{r}
install.packages("remotes")
```

```{r}
remotes::install_cran(c("pct", "osmextract", "osmdata", "stats19", "tidyverse", "tmap", "skimr"))
```

You can load them as follows:

```{r}
library(pct)
library(stats19)
library(tidyverse)
library(tmap)
# tmap_mode("view") # uncomment this for interactive maps
tmap_mode("plot")
```

## Cycling behaviour and potential

```{r}
# https://github.com/npct/pct-outputs-regional-notR/blob/master/commute/lsoa/south-yorkshire/rnet_full.geojson
cycle_trips_network_estimates = get_pct_rnet(region = "south-yorkshire")
zones = get_pct_zones("south-yorkshire")
```

You can plot this data in a static map as follows:

```{r, out.width="50%", fig.show='hold'}
zones %>% 
  select(lad_name) %>% 
  plot()
cycle_trips_network_estimates %>%
  select(dutch_slc) %>% 
  plot()
```

Let's subset the data representing Sheffield.

```{r}
zones_sheffield = zones %>% 
  filter(lad_name == "Sheffield")
```

```{r}
rnet_sheffield = cycle_trips_network_estimates[zones_sheffield, ]
```

```{r}
rnet_sheffield %>% 
  tm_shape() +
  tm_lines(lwd = "ebike_slc", scale = 9)

```

## Getting the infrastructure data

```{r}
extra_tags = c("maxspeed", "bicycle")
osm_data_region = osmextract::oe_get_network(place = "south yorkshire", mode = "cycling", extra_tags = extra_tags)
osm_sheffield = osm_data_region[zones_sheffield, ]
```

```{r}
osm_sheffield %>% 
  sf::st_drop_geometry() %>% 
  skimr::skim()
```

```{r}
osm_cycleways = osm_sheffield %>% 
  filter(highway == "cycleway")
```

```{r}
qtm(osm_cycleways)
```


